Finite element analysis ofmulti-dimensional and simplifiedmodels for beams and plates

### 2023-11-15 files/Chapter5/3D_FEM.tex
symbols
table of symbols
Chapter 6

\subsubsection{Reference configuration for rectangular cross-section}
Let $\{e_1,e_2,e_3\}$ be a right-handed orthonormal basis for $R^3$. Denote the elastic body as $\Omega \in R^3$ with $(0,0,0)$ the point of reference. For a rectangular cross-section, the body $\Omega$ can be described as
\begin{eqnarray*}
	\Omega = \left\{ x \in R^3 \ | \ 0 \leq x_1 \leq 1, \ -\frac{h}{2} \leq x_2 \leq \frac{h}{2} , \ -\frac{b}{2} \leq x_3 \leq \frac{b}{2}\right \}
\end{eqnarray*}
Let $\partial \Omega$ denote the boundary of the body. Divide $\partial \Omega$ into the six distinct flat surfaces as follows:

@@

\subsection{System of ordinary differential equations}
Consider the following standard Finite Element Method matrices.

>>>>

\subsubsection{Reference configuration for rectangular cross-section}
Let $\{e_1,e_2,e_3\}$ be a right-handed orthonormal basis for $R^3$. Denote the elastic body as $\Omega \in R^3$ with $(0,0,0)$ the point of reference. For a rectangular cross-section, the body $\Omega$ can be described as
\begin{eqnarray*}
	\Omega = \left\{ x \in R^3 \ | \ 0 \leq x_1 \leq 1, \ -\frac{h}{2} \leq x_2 \leq \frac{h}{2} , \ -\frac{b}{2} \leq x_3 \leq \frac{b}{2}\right \}
\end{eqnarray*} \label{sym:width}
Let $\partial \Omega$ denote the boundary of the body. Divide $\partial \Omega$ into the six distinct flat surfaces as follows:

@@

\subsection{System of ordinary differential equations}\label{3d_fem_g}
Consider the following standard Finite Element Method matrices.

### 2023-11-15 files/Chapter5/PlateModel.tex
table of symbols
Chapter 6

Denote the elastic body as $\Omega \in R^2$ with the reference point $(0,0)$. For a rectangular plate,
\begin{eqnarray*}
	\Omega = \left \{ x \in R_2 \ | \ 0 \leq x_1 \leq 1, \ 0 \leq x_2 \leq b \right \}.
\end{eqnarray*}
Let $\partial \Omega$ denote the boundary of plate. The boundary $\partial \Omega$ can be divided into four distinct lines.

@@

For all $f,g \in T_1(\Omega)\times T_2(\Omega) $, define the bilinear forms
\begin{eqnarray*}
	c(f,g) & = & h(f_1,g_1)_{\Omega} + I(f_2,g_2)_{R_2} \\
	b^*(f,g) & = & b(f_2,g_2) + h(\nabla f_1 + f_2, \nabla g_1 + g_2)_{R_2}
\end{eqnarray*}
where the integrals are defined by
\begin{eqnarray*}
	(f_1,g_1)_{\Omega} & = & \iint_\Omega f_1 g_1 \ dA,\\
	(f,g)_{R_2} & = & \iint_\Omega f \cdot g \ dA.
\end{eqnarray*}

@@

Denote the space $X = L^2(0,1)\times L^2(0,1)^2$ as a setting for Problem P-1V. A natural inner product for $X$ is $(f,g)_X = (f_1,g_1)_{\Omega} + (f_2,g_2)_{R_2}$.  Define $W$ as the space $X$ with the inner product $c$ and $V = V_1(0,1) \times V_2(0,1)$

@@

\subsection{System of ordinary differential equations}
The standard FEM matrices $K_{11}$, $K_{12}$, $K_{21}$, $K_{22}$ and $M_F$ where presented in section \ref{ssec:2DFEM:DE}. Even though the definition of $R_2$ is different in section \ref{sec:FEM:2D}, the definition of the matrices are the same and are not repeated here.

>>>>

Denote the elastic body as $\Omega \in R^2$ with the reference point $(0,0)$. For a rectangular plate,
\begin{eqnarray*}
	\Omega = \left \{ x \in R^2 \ | \ 0 \leq x_1 \leq 1, \ 0 \leq x_2 \leq b \right \}.
\end{eqnarray*}
Let $\partial \Omega$ denote the boundary of plate. The boundary $\partial \Omega$ can be divided into four distinct lines.

@@

For all $f,g \in T_1(\Omega)\times T_2(\Omega) $, define the bilinear forms
\begin{eqnarray*}
	c(f,g) & = & h(f_1,g_1)_{\Omega} + I(f_2,g_2)_{R^2} \\
	b^*(f,g) & = & b(f_2,g_2) + h(\nabla f_1 + f_2, \nabla g_1 + g_2)_{R^2}
\end{eqnarray*}
where the integrals are defined by
\begin{eqnarray*}
	(f_1,g_1)_{\Omega} & = & \iint_\Omega f_1 g_1 \ dA,\\
	(f,g)_{R^2} & = & \iint_\Omega f \cdot g \ dA.
\end{eqnarray*}

@@

Denote the space $X = L^2(0,1)\times L^2(0,1)^2$ as a setting for Problem P-1V. A natural inner product for $X$ is $(f,g)_X = (f_1,g_1)_{\Omega} + (f_2,g_2)_{R^2}$.  Define $W$ as the space $X$ with the inner product $c$ and $V = V_1(0,1) \times V_2(0,1)$

@@

\subsection{System of ordinary differential equations}\label{plate_fem_g}
The standard FEM matrices $K_{11}$, $K_{12}$, $K_{21}$, $K_{22}$ and $M_F$ where presented in section \ref{ssec:2DFEM:DE}. Even though the definition of $R^2$ is different in section \ref{sec:FEM:2D}, the definition of the matrices are the same and are not repeated here.
